---
title: "System_Fonts"
author: "GranPiero"
date: "2024-04-08"
categories: [it]
execute: 
  echo: false
format: pdf
pdf-engine: xelatex
mainfont:   CenturySchL-Roma
fontsize: 12pt
---

### Fetch Fonts from Windows

-   in *Control Panel\\All Control Panel Items\\Fonts* or *C:\\Windows\\Fonts*

-   copy to *C:\\\_myHUL\\VOL\\RS\\\_EXT\\myFONTS*

### Install Fonts on Linux

-   i.e. inside Docker /WSL

-   https://www.google.com/search?q=how+to+install+a+font+on+gnu%2Blinux

-   Most Linux distributions store the system-wide fonts in the "/usr/share/fonts" directory.

### script

sudo mkdir /usr/share/fonts/truetype/arial

cd /home/rstudio/EXT/\_myFONTS/Arial

sudo mv *.ttf /usr/share/fonts/truetype/arial*

*sudo fc-cache -f -v*

*sudo chgrp rstudio arial + sudo chown rstudio arial*

*sudo chown rstudio* .ttf + sudo chgrp rstudio \*.ttf

fc-match arial

```{r, PRE}
library(data.table)
showtext::showtext_auto()
```

This result was proved in \cite{jones.1967}.

```{=tex}
\begin{tabular}{|l|l|}\hline
Age & Frequency \\ \hline
18--25  & 15 \\
26--35  & 33 \\
36--45  & 22 \\ \hline
\end{tabular}
```
This manipulates system_fonts

```{r}
fonts <- systemfonts::system_fonts() |>
  data.table::data.table()
```

```{r, FAMILY}
fonts[,.N,family][order(family)] |>
  tibble::rowid_to_column("ID") |>
  gt::gt() |>
  gt::tab_header("System Fonts available here")
```

```{r, NAMES}
fonts[family %like% "Arial|Century",.N,.(family,name)][order(family)] |>
  tibble::rowid_to_column("ID") |>
  gt::gt() |>
  gt::tab_header("System Fonts available here")
```
