---
title: "System_Fonts"
author: "GranPiero"
date: "2024-04-08"
categories: [it]
execute: 
  echo: false
format: pdf
pdf-engine: xelatex
mainfont: "TeX Gyre Schola"
fontsize: 12pt
---

mainfont: "texgyreschola-regular.otf"

mainfont: "TeX Gyre Schola"

KO mainfont: "Century Schoolbook L Roman"

### Fetch Fonts from Windows

- in *Control Panel\\All Control Panel Items\\Fonts* or *C:\\Windows\\Fonts*

- copy to *C:\\\_myHUL\\VOL\\RS\\\_EXT\\myFONTS*

### Install Fonts on Linux

- i.e. inside Docker /WSL

- https://www.google.com/search?q=how+to+install+a+font+on+gnu%2Blinux

- Most Linux distributions store the system-wide fonts in the "/usr/share/fonts" directory.

- for CenturySchL-Roma follow three lines

- mkdir -p \~/.local/share/fonts

- cp \*.otf \~/.local/share/fonts/

- fc-cache -f

### script

sudo mkdir /usr/share/fonts/truetype/arial

cd /home/rstudio/EXT/\_myFONTS/Arial

sudo mv *.ttf /usr/share/fonts/truetype/arial*

*sudo fc-cache -f -v*

*sudo chgrp rstudio arial + sudo chown rstudio arial*

*sudo chown rstudio* .ttf + sudo chgrp rstudio \*.ttf

fc-match arial

```{r, PRE}
library(data.table)
showtext::showtext_auto()
```

This result was proved in \cite{jones.1967}.

\begin{tabular}{|l|l|}\hline
Age & Frequency \\ \hline
18--25  & 15 \\
26--35  & 33 \\
36--45  & 22 \\ \hline
\end{tabular}

This manipulates system_fonts

```{r}
fonts <- systemfonts::system_fonts() |>
  data.table::data.table()
```

```{r, FAMILY}
fonts[,.N,family][order(family)] |>
  tibble::rowid_to_column("ID") |>
  gt::gt() |>
  gt::tab_header("System Fonts available here")
```

```{r, NAMES}
library(data.table)
fonts[family %like% "Arial|Century",.N,.(family,name)][order(family)] |>
  tibble::rowid_to_column("ID") |>
  gt::gt() |>
  gt::tab_header("System Fonts available here")
```

Andale Mono Arial Arial Black C059 Century Schoolbook L Comic Sans MS Courier New D050000L Georgia Impact Lato Lato,Lato Black Lato,Lato Hairline Lato,Lato Heavy Lato,Lato Light Lato,Lato Medium Lato,Lato Semibold Lato,Lato Thin Nimbus Mono PS Nimbus Roman Nimbus Sans Nimbus Sans Narrow P052 Roboto Roboto Condensed Roboto Condensed,Roboto Condensed Light Roboto Condensed,Roboto Condensed Medium Roboto,Roboto Black Roboto,Roboto Light Roboto,Roboto Medium Roboto,Roboto Thin Standard Symbols PS TeX Gyre Adventor TeX Gyre Bonum TeX Gyre Chorus TeX Gyre Cursor TeX Gyre Heros TeX Gyre Heros Cn TeX Gyre Pagella TeX Gyre Schola TeX Gyre Termes Times New Roman Trebuchet MS URW Bookman URW Gothic Verdana Webdings Z003

### Sources

## Summary Table (by source)

| Source / Foundry | Fonts |
|----|----|
| **Microsoft / Monotype** | Andale Mono, Arial, Arial Black, Comic Sans MS, Courier New, Georgia, Impact, Times New Roman, Trebuchet MS, Verdana, Webdings |
| **Google Fonts** | Lato (all variants), Roboto (all variants), Roboto Condensed (all variants) |
| **URW++ / Ghostscript** | C059, Century Schoolbook L, D050000L, Nimbus Mono PS, Nimbus Roman, Nimbus Sans, Nimbus Sans Narrow, P052, Standard Symbols PS, URW Bookman, URW Gothic, Z003 |
| **TeX Gyre (based on URW)** | Adventor, Bonum, Chorus, Cursor, Heros, Heros Cn, Pagella, Schola, Termes |

All variants are downloadable from Google Fonts:

### **Lato (all variants)**

<https://fonts.google.com/specimen/Lato>

### **Roboto (all variants)**

<https://fonts.google.com/specimen/Roboto>

### **Roboto Condensed (all variants)**

`https://fonts.google.com/specimen/Roboto+Condensed` [(fonts.google.com in Bing)](https://www.bing.com/search?q=%22https%3A%2F%2Ffonts.google.com%2Fspecimen%2FRoboto%2BCondensed%22)

### **Ghostscript URW font collection**

<https://ghostscript.com/fonts.html> (Direct download: `https://github.com/ArtifexSoftware/urw-base35-fonts` [(github.com in Bing)](https://www.bing.com/search?q=%22https%3A%2F%2Fgithub.com%2FArtifexSoftware%2Furw-base35-fonts%22) )

### **SourceForge: corefonts**

This is the *officially permitted redistribution* of the original Microsoft installers.

🔗 `https://sourceforge.net/projects/corefonts/files/the%20fonts/final/` [**(sourceforge.net in Bing)**](https://www.bing.com/search?q=%22https%3A%2F%2Fsourceforge.net%2Fprojects%2Fcorefonts%2Ffiles%2Fthe%2520fonts%2Ffinal%2F%22)

ttf-mscorefonts-installer

- To [install Microsoft fonts on Ubuntu](https://www.wikihow.com/Install-TrueType-Fonts-on-Ubuntu#Installing-Microsoft-Fonts-on-Ubuntu), use the command "sudo apt install ttf-mscorefonts-installer".

cd \~/.fonts for f in adventor bonum chorus cursor heros heroscn pagella schola termes; do wget <https://www.gust.org.pl/projects/e-foundry/tex-gyre/$f.zip> unzip \$f.zip donels
